---
title: "sparkvis"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**sparkvis** adds the necessary methods to **ggvis** to allow it to handle **sparklyr's** *tbl_spark* class data sets.  

One of the methods is a **compute_bin** variance to calculate a histogram's bins inside Spark and then collect results, thus reducing the amount of data brought over into memory.  **Limitation**: The function only works with straigth column names not formulas, so while *~mpg* will work, *~factor(am)* will not.

Future plans are to create more compute methods that will open other layers to *tbl_spark* data sets.

### Installation

You can install **sparkvis** from GitHub

```{r, eval = FALSE}
devtools::install_github("edgararuiz/sparkvis")
```

### Load needed libraries


```{r, eval = FALSE}
library(sparklyr)
library(ggvis)
library(sparkvis)
```

```{r, include = FALSE, eval = TRUE}
library(sparklyr)
library(ggvis)
library(sparkvis)
```

### Create a new Spark connection

```{r}
conf <- spark_config()
conf$`sparklyr.shell.driver-memory` <- "8G"
sc <- spark_connect(master="local", config = conf, version = "2.1.0")
```

### Copying mtcars to the Spark environment

```{r}
spark_mtcars <- copy_to(sc, mtcars)
```

### Comparison

#### Using a standard data frame

```{r}
mtcars %>% 
  ggvis(~mpg) %>% 
  layer_histograms(width = 5, stack = FALSE) 
```

#### Now using a Spark table


```{r}
spark_mtcars %>% 
  ggvis(~mpg) %>% 
  layer_histograms(width = 5, stack = FALSE) 
```

### Closing connection

```{r}
spark_disconnect(sc)
```
